---
title       : Developing Data Products
subtitle    : my shinyapp
author      : yaleidu
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Ideas of my app
### Problem
```{r echo=FALSE, message=FALSE}
require(knitr)
opts_chunk$set(message = FALSE, fig.align = 'center', warning = FALSE, comment = NA)
```

There is a classification algorithm named `KNN(k-Nearest Neighbor algorithm)`, which use one's 
neighbours to predict an unkown sample.

This algorithm is quite simple and useful, the only problem is use how many neighbours to predict?

--- 
## Ideas of my app
### Solution

Derictly, we can use a bunch of parameters to build a model, and choose the best one.

The best means the one has smallest misclassification rate.

--- 
## Ideas of my app
### Dataset
Here I use the famous data set `iris` in R, which has five variables.
```{r}
head(iris)
```

We will use the four predictors `r colnames(iris)[1:4]` to predict `r colnames(iris)[5]`

--- 
## Ideas of my app
### Result

```{r echo=FALSE}
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  require(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

```{r echo=FALSE, message=FALSE, fig.align='center', fig.height=7, fig.width=12}
library(ggplot2)
library(class)
group = iris$Species
train = iris[, 1:4]
out_plot = function(x){
    predictSpecies = knn(train, train, group, k = x)
    iris2 = cbind(iris, predictSpecies)
    out = ggplot(data=iris2, aes(Sepal.Length, Sepal.Width)) + 
        geom_point(aes(color=predictSpecies, shape=predictSpecies), size=3) +
        geom_point(data=subset(iris2, predictSpecies!=Species), 
                   aes(Sepal.Length, Sepal.Width), 
                   shape=5, size=5, col='red')+
        ggtitle(paste0('k=', x))
}

multiplot(out_plot(2), 
          out_plot(5), 
          out_plot(10), 
          out_plot(20), cols=2)
```




